Analysis methods for characterizing the climate sensitivity of annual growth and woody productivity using tree-rings

### 2020-03-16 methods/analysis_methods.Rmd
update analysis methods

These are outlined below ("Current methodology"), with additional considerations and alterative approaches outlined later ("Considerations and alternative approaches")

@@

2.2. For each species independently, run GAM models including every combination of climate variable, DBH, and splines on year fit to each individual.

>>>>

These are outlined below ("Current methodology"), with additional considerations and alterative approaches outlined later ("Considerations and alternative approaches").

R script is here: https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/scripts/Analysis.R. (ask KAT for access if you can't access)

@@

2.2. For each species independently, run GAM models including every combination of climate variable, DBH, and splines on year fit to each individual.
`ln[response variable] ~ DBH + [climate variables] + year (spline) + tag (random effect)`
